Elaboration with First-Class Implicit Function Types

### 2020-05-22 paper.tex
update line counts

We provide an implementation of the elaborator from Section
\ref{sec:extending_elaboration}. It is a standalone Haskell program which reads
a surface expression from standard input, and outputs the result of elaboration,
or optionally the type or the normal form of the result. It is implemented in
1056 lines of Haskell. Of this, 669 lines constitute the core syntax,
evaluation, unification and elaboration. Of these 669 lines, 454 lines implement
the basic elaborator of Section \ref{sec:bidirectional_elaboration} and 215
lines implement the extended elaborator.

>>>>

We provide an implementation of the elaborator from Section
\ref{sec:extending_elaboration}. It is a standalone Haskell program which reads
a surface expression from standard input, and outputs the result of elaboration,
or optionally the type or the normal form of the result. It is implemented in
1106 lines of Haskell. Of this, 677 lines constitute the core syntax,
evaluation, unification and elaboration. Of these 669 lines, 462 lines implement
the basic elaborator of Section \ref{sec:bidirectional_elaboration} and 215
lines implement the extended elaborator.
